### 2021-03-25 Chapter-2/Chapter-2.tex
Updates from Overleaf

Based on the above attacks, some work~\cite{brickell2011technologies} suggests not having secret-dependent memory accesses at coarser than cache line granularity should be secure enough. However, recent studies shows that having memory accesses within a cache line is also dangerous. One example is the CacheBleed attack~\cite{yarom2017cachebleed}. It is a cache channel attack can exploits cache-back collisions.
\subsection{Page-level Channel}
Page channel attacks can observe the memory access at the granularity of memory pages. One example is the controlled-channel attack~\cite{xu2015controlled}, where a privileged adversary try to infer the sensitive information by manipulating the enclave page access. Those kinds of attacks usually happen on the shielding system. A malicious OS can proactively revoke a virtual enclave memory page from the memory. If the victim enclave program accesses the memory table, then the adversary can know which page is accessed by observing the page fault sequences. While the granularity of the controlled-channel attacks is coarse-grained, the controlled-channel attacks allow the attacker to have a noise-free observation. Other examples like the TLB side-channel attack, DDRAM attacks share the same page-level granularity.

@@

\subsection{Target Applications}
While there is a vast number of studies\cite{yarom2017cachebleed,191010,184415,Osvik2006,liu2015last} on side-channel attacks and detections, we find many of those work targets on the encryption key on cryptography libraries. In terms of the non-cryptography side-channel attacks. We find many of them can be classified into the below three categories.

>>>>

Based on the above attacks, some work~\cite{brickell2011technologies} suggests not having secret-dependent memory accesses at coarser than cache line granularity should be secure enough. However, recent studies shows that having memory accesses within a cache line is also dangerous. One example is the CacheBleed attack~\cite{yarom2017cachebleed}. It is a cache channel attack can exploits cache-back collisions.
\subsection{Page-level Channel}
Page channel attacks allow an attacker can observe the memory access at the granularity of memory pages. One example is the controlled-channel attack~\cite{xu2015controlled}, where a privileged adversary try to infer the sensitive information by manipulating the enclave page access. Those kinds of attacks usually happen on the shielding system. A malicious OS can proactively revoke a virtual enclave memory page from the memory. If the victim enclave program accesses the memory table, then the adversary can know which page is accessed by observing the page fault sequences. While the granularity of the controlled-channel attacks is coarse-grained, the controlled-channel attacks allow the attacker to have a noise-free observation. Other examples like the TLB side-channel attack, DDRAM attacks share the same page-level granularity.

@@

\subsection{Target Applications}
While there is a vast number of studies\cite{yarom2017cachebleed,191010,184415,Osvik2006,liu2015last} on side-channel attacks, we find many of those work targets on the encryption key on cryptography libraries. We find current side-channel attacks can be classified into the below three categories.
